---
title: "Fruit snack analysis"
author: "Karl Broman"
date: 2015-02-14
#output: html_document
#output:
#  pdf_document:
#    fig_width: 7
#    fig_height: 6
#    fig_caption: true
---

```{r options, include=FALSE}
#knitr::opts_chunk$set(fig.width=12, fig.height=5,
#                      echo=FALSE, results="hide",
#                      message=FALSE, warning=FALSE)
#barcolor <- "#E6E6FA" # Lavender
#set.seed(33377561)
```

```{r load_packages, include=FALSE}
library(gapminder)
library(ggplot2)

theme_set(theme_bw())
```

```{r simple_plot, fig.cap="this is figure 3.16 from https://socviz.co/makeplot.html"}
p <- ggplot(data = gapminder, mapping = aes(x = gdpPercap, y = lifeExp))
p + geom_point(mapping = aes(color = continent)) +
    geom_smooth(method = "loess") +
    scale_x_log10()
```

```{r saving_plot, include=FALSE}
ggsave("myplot.png")
```
```

This is 4.4 in https://socviz.co/groupfacettx.html:

```{r}
p <- ggplot(data = gapminder, mapping = aes(x = year, y = gdpPercap))
p + geom_line(color="gray70", aes(group = country)) +
    geom_smooth(size = 1.1, method = "loess", se = FALSE) +
    scale_y_log10(labels=scales::dollar) +
    facet_wrap(~ continent, ncol = 5) +
    labs(x = "Year",
         y = "GDP per capita",
         title = "GDP per capita on Five Continents")
```


## Testing something else

A text ...

```{r butterfat-densitites, fig.cap='Some caption in here'}
p <- ggplot(data = midwest,
            mapping = aes(x = area, fill = state, color = state))
p + geom_density(alpha = 0.3)
```
